Creating Data for "Social inequality in mortality among adults and elderly in northern Sweden 1850--2013"\footnote{Version 2017-05-27.}

### 2017-06-07 CreateData/creDat.Rnw
koll

\title{Creating Data for "Social inequality in mortality among
  adults and elderly in northern Sweden 1850--2013"\footnote{Paper presented
    at CEDAR, 27 April 2017,
    Version 2017-03-28.}}

\date{March 28, 2017}

>>>>

\title{Creating Data for "Social inequality in mortality among
  adults and elderly in northern Sweden 1850--2013"\footnote{Version 2017-05-27.}}

\date{\today}
